Equations & R Code

### 2016-12-13 manuscript/coexistence-stability_ms.Rmd
updates equation 2; maybe wrong
first edits from FRA added

\begin{abstract}
Theory relating species richness to ecosystem stability typically ignores the potential for environmental variability to promote species coexistence.
Failure to account for fluctuation-dependent coexistence mechanisms may explain observed deviations from the expected positive diversity-stability relationship, and limits our ability to predict the consequences of future increases in environmental variability.
We use a consumer-resource model to explore how coexistence via the temporal storage effect and relative nonlinearity affects ecosystem stability.
We show that a negative, rather than positive, diversity-stability relationship is possible when ecosystem function is sampled across a natural gradient in environmental variability and diversity.
We also show how fluctuation-dependent coexistence can buffer ecosystem functioning against increasing environmental variability by promoting species richness and portfolio effects.
Our work provides a general explanation for variation in observed diversity-stability relalationships and highlights the importance of conserving regional species pools to help buffer ecosystems against predicted increases in environmental variability.
\vspace{2em}
\end{abstract}

@@

However, the ability of biodiversity-ecosystem functioning (BEF) experiments to accurately represent real-world dynamics is debated [@Wardle2016; @Eisenhauer2016].
Much of the debate centers around the fact BEF experimental protocols do not allow species gains to offset species losses.
Theoretical work on diversity-stability relationships typically suffers from the same limitation: it recognizes the role of environmental variability in driving population fluctuations which destabilize ecosystems, but ignores the potential for environmental variability to promote species richness and thereby help stabilize ecosystems [Loreau 2010, but see @Chesson2001].

@@

MATERIALS AND METHODS
---------------------
###  Consumer-resource model
We developed a semi-discrete consumer-resource model that allows many species to coexist on one resource by either the storage effect or relative nonlinearity. 
In our model, the consumer can be in one of two-states: a dormant state $D$ and a live state $N$.
The dormant state could represent, for example, the seedbank of an annual plant.
Transitions between $N$ and $D$ occur at discrete intervals $\tau$ with continuous-time consumer-resource dynamics between discrete transitions. 
Thus, our model is formulated as "pulsed differential equations" [@Pachepsky2008; @Mailleret2009; @Mordecai2016]. 
For clarity we refer to $\tau$ as years and the growing time between years as seasons with daily ($t$) time steps.

@@

\begin{align}
\frac{\text{d}N_{i}}{\text{d}t} &= N_{i}\epsilon_if_{i}(R), \quad t \ne \tau_k\\
\frac{\text{d}R}{\text{d}t} &= - \sum\limits_{i=1,2}f_{i}(R)N_{i}, \quad t \ne \tau_k
\end{align}

@@

\noindent where $D(\tau_k)$, $N(\tau_k)$, and $R(\tau_k)$ are the abundances of each state at the end of growing season *k* and $\tau_k^+$ denotes the beginning of growing season $k=1$. 
The activation of dormant biomass to live biomass is controlled by $\gamma$, which is year (*k*) and species (*i*) specific.
Dormant biomass is equal to a constant fraction ($\alpha$) of live biomass at the end of the previous season ($N_{i}(\tau_k)$), plus survival ($1-\eta_i$) of dormant biomass ($D_{i}(\tau_k)$) at the end of the previous year and dormant biomass remaining after live biomass activation ($D_{i}(\tau_k)(1-\gamma_{i,\tau_k})$).
Live biomass is equal to newly activated dormant biomass ($\gamma_{i,t}[D_{i}(\tau_k)$), minus some fraction of live biomass that is converted to dormant biomass ($(1-\alpha_i)N_{i}(\tau_k)$)
We assume the resource pool is not replenished within a growing season.
Resource replenishment occurs between growing seasons, and the resource pool (*R*) at the start of the growing season *k*+1 is $R(\tau_k^+) = R^+$, where $R^+$ is a random resource pulse drawn from a log-normal distribution with mean $\mu(R^+)$ and standard deviation $\sigma(R^+)$. 
Model parameters and notation are described in Table 1.

@@

\begin{align}
\Sigma(\gamma) = 
\begin{bmatrix}
\sigma^2_{E} & \rho_{1,2}\sigma^2_{E} & \rho_{1,3}\sigma^2_{E} & \rho_{1,4}\sigma^2_{E} \\
\rho_{2,1}\sigma^2_{E} & \sigma^2_{E} & \rho_{2,3}\sigma^2_{E} & \rho_{2,4}\sigma^2_{E} \\
\rho_{3,1}\sigma^2_{E} & \rho_{3,2}\sigma^2_{E} & \sigma^2_{E}  & \rho_{3,4}\sigma^2_{E} \\
\rho_{4,1}\sigma^2_{E} & \rho_{4,2}\sigma^2_{E} & \rho_{4,3}\sigma^2_{E} & \sigma^2_{E}  \\
\end{bmatrix}
\end{align}

\noindent where $\sigma^2_{E}$ is the variance of the environmental cue and $\rho_{i,j}$ is the correlation between between the species *i*'s and species *j*'s transition rates. 
$\rho$ must be less than 1 for stable coexistence, and in all simulations we placed that constraint that $\rho_{i,j} = \rho_{j,i}$ for each species pair.
The inferior competitor has the strongest potential to persist when $\rho=-1$ (perfectly uncorrelated transition rates). 
We used the ```R``` function ```mvrnorm``` to generate sequences of (un)correlated variates *E* that we converted to germination rates in the 0-1 range: $\gamma = e^E / 1 + e^E$.
Note that $\Sigma(\gamma)$ must be positive definite.
So, after defining $\Sigma(\gamma)$ with all $\rho_{i,j}$s and $\sigma^2_{E}$, we used the ```nearPD``` function from the ```Matrix``` package in ```R``` to coerce the variance-covariance matrix to be positive definite.

@@

For example, in Fig. 1C we show two species' resource uptake curves that are relatively nonlinear.
Species B has the lowest $R^*$ and would competitively exclude species A in the absence of environmental fluctuations.
But, fluctuating resource supplies can benefit species A because it can take advantage of relatively high resource levels due its higher saturation point.
Stable coexistence is only possible, however, if each species creates a disadvantage for itself when abundant.
This occurs in our model because when a resource conservative species (e.g., species B in Fig. 1C) is abundant, resource levels will remain high for a longer period of time because its draw down of resources starates.
Likwise, when a resource acquisitive species (e.g., species A in Fig. 1C) is abundant, it quickly draws down resources to levels that favor resource conservative species.
Such reciprocity ensures species can increase when rare and stablizes coexistence [@Armstrong1980; @Chesson2000; @Chesson2004].

@@

Under relative nonlinearity, species' resource response curves (Fig. S1-1) reflect traits that determine the intrinsic stability of each species.
Therefore, we ran two sets of simulations for relative nonlinearity: one where the species pools increased from stable to unstable species and vice versa.
For example, if species A is the most stable species and species D is the least stable we ran simulations where the species pool increased from one to four species as A then B then C then D.
We then ran simulations with that order reversed.

All simulations were run for 5,000 seasons with 20-day growing seasons. 
We averaged biomass over the growing season, and those yearly values were used to calculate total community biomass in each year.
After discarding an initial 500 seasons to reduce transient effects on our results, we calculated the coffecient of variation (*CV*) of summed species biomass through time, which represents ecosystem variability,  the inverse of ecosystem stability.
We calculated species richness as the number of species whose average biomass was greater than 1 over the course of the simulation.
Parameter values for specific results are given in figure captions.
Within-season dynamics were solved given initial conditions using the package ``deSolve`` [@Soetaert2010] in ``R`` [@Team2013].
```R``` code for our model function is in the Supporting Information Appendix S1.
All model code has been deposited on Figshare (*link*) and is available on GitHub at http://github.com/atredennick/Coexistence-Stability.

@@

When we performed species removals but held environmental variability at given levels, we found the typical negative diversity-variability relationship (Fig. 2B,D).
The relationship was very constrained for the storage effect because all species have similar temporal variances.
Therefore, regardless of species identity, having more species will always stabilize ecosystem functioning through portfolio effects.
On the contrary, the relationship was weaker for relative nonlinearity (Fig. 2D) because each species has unique temporal variance depending on its resource uptake curve.
Depending on the specific combination of species, two-species communities were sometimes less variable than three-species communities.

@@

The dampening effect of fluctuation-dependent coexistence on increasing environmental variability depends on the specific traits (parameter values) of the species in the regional pool.
Asymmetric competition makes it more difficult for new species to enter the local community (Fig. 3; compare top and bottom panels).
Relatively high competition also increases the rate at which ecosystem *CV* increases with environmental variance (Fig. S1-3) because the abundance of inferior competitors is reduced and therefore does not influence ecosystem *CV* as much as when competition is symmetric.
The correlation of species' environmental responses also mediates the relationship between environmental variance, species richness, and ecosystem *CV*: lower correlations make it easier for new species to enter the community and unique environmental responses are always stabilizing (Fig. 3).

@@

DISCUSSION
----------
Theory developed for biodiversity-ecosystem function experiments emphasizes that increases in species richness should reduce ecosystem variability. 
Consistent with theoretical expectations from models in which species coexistence is maintained by fluctuation-independent mechanisms, we produced the typical negative diversity-variability relationship (Fig. 2B,D) from a model with fluctation-dependent species coexistence [also see @Chesson2001].
Likewise, our results from the species removal simulations are consistent with results from biodiversity-ecosystem functioning experiments showing a negative relationship between species richness and ecosystem variability.
This is encouraging because species almost certainly coexist by some combination of fluctuation-independent (e.g., resource partitioning) and fluctuation-dependent mechanisms.
By extending theory to communities where species richness is explicitly maintained by temporal variability, we have gained confidence that experimental findings are generalizable to many communities.
In other words, in local settings where environmental variability is relatively homogenous, reductions in the number of species will reduce the stability of ecosystem functioning, regardless of how coexistence is maintained.

When we allowed a gradient of environmental variability to determine species coexistence, we discovered a positive relationship between species richness and ecosystem variability (Fig. 2A,C).
While surprising when viewed through the lens of previous theory and experimental findings, such a relationship is a direct consequence of how diversity can be maintained in fluctuating environments.
The storage effect and relative nonlinearity both require envrionmental fluctuations to allow niche differentiation between species pairs [@Chesson2000].
Therefore, species coexistence gains strength, for both mechanisms, as the environment becomes more variable (Fig. S1-2), but the increase in environmental variability also increases ecosystem variability.

Our results may explain why deviations from the negative diversity-variability relationship often come from observational studies [@Jiang2009].
Observational studies must rely on natural diversity gradients, and if species richness depends on environmental variability, it is entirely possible to observe positive diversity-variability relationships.
For example, Sasaki and Lauenroth (2011) found a negative relationship between species richness and the temporal stability of plant abundance (a positive diversity-variability relationship) in a semi-arid grassland.
Their data came from a six sites that were 6 km apart.
While Sasaki and Lauenroth explained their results in terms of dominant species' effects, it is also possible that each site experienced slightly different levels of environmental variability that influenced species coexistence.
@DeClerck2006 also found a positive diversity-variability when sampling conifer richness and the variability of productivity across a large spatial gradient in the Sierra Nevada.

@@

\begin{table}[!htbp]
\footnotesize
\caption{Default values of model parameters and their descriptions. Parameters that vary depending on the mode and strength of species coexistence or depending on species copmetive hierarchies are labeled as "variable" in parantheses. The dormant-to-live biomass transition fraction ($\gamma$) is a function of other parameters, so has no default value.}
\begin{tabular}{l l l}
\hline
Parameter & Description & Value \\
\hline
$r$ & maximum per capita growth rate & 1 (variable) \\
$a$ & Hill function rate parameter & 2 (variable) \\
$b$ & Hill function curvature parameter & 2.5 (variable) \\
$\epsilon$ & resource-to-biomass conversion efficiency & 0.5 \\
$\alpha$ & allocation fraction of live biomass to dormant biomass & 0.5 (variable) \\
$\gamma$ & dormant-to-live biomass transition fraction & -- \\
$\rho$ & correlation of species' response to the environment & 0 (variable) \\
$\sigma_E$ & variance of the environmental cue & 2 (variable) \\
$\eta$ & dormant biomass mortality rate & 0.1 \\
$\mu(R^+)$ & mean annual resource pulse & 20 (non-log scale) \\
$\sigma(R^+)$ & standard deviation of annual resource pulse & 0 (variable) \\
\hline
\end{tabular}
\end{table}

@@

\begin{figure}[!ht]
  \centering
      \includegraphics{./components/main_figure_hires.png}
  \caption{Variability of total community as function of species richness when coexistence is maintained by the storage effect (A,B) or relative nonlinearity (C,D). Top panels show results from simulations where environmental or resource variance determine the number species that coexist in a community. Bottom panels show results from simulations where environmental or resource variance is fixed at a level that allows coexistence of all four species, but speces are removed to manipulate diversity. The top panels represent regional diversity-stability relationships across natural diversity gradients, whereas the bottom panels represent local diversity-stability relationships.}
\end{figure}

@@

\begin{figure}[!ht]
  \centering
      \includegraphics[height=4in]{./components/coexistence_stability_infographic_v2.png}
  \caption{Example of how species additions under increasing environmental variability can buffer ecosystem stability when species coexistence is fluctuation-dependent via the storage effect. Environmental variability ($\sigma^2_E$) increases linearly with time. (A) Time series of species' biomasses (colored lines) in a closed community where colonization of new species is not possible and (B) its associated coefficient of variation (Rolling CV; calculated over 100-yr moving window) through time. (C) Time series of species' biomasses in an open community where colonization by new species from the regional pool of four species becomes possible as environmental variation increases. The trajectory of total biomass CV in the open community (D) asymptotes at lower variability than in the closed community (B) due to the buffering effect of species richness.}
\end{figure}

>>>>

\begin{abstract}
Theory relating species richness to ecosystem stability typically ignores the potential for environmental variability to promote species coexistence.
Failure to account for fluctuation-dependent coexistence mechanisms may explain observed deviations from the expected positive diversity-stability relationship, and limits our ability to predict the consequences of future increases in environmental variability.
We use a consumer-resource model to explore how coexistence via the temporal storage effect and relative nonlinearity affects ecosystem stability.
We show that a negative, rather than positive, diversity-stability relationship is possible when ecosystem function is sampled across a natural gradient in environmental variability and diversity.
We also show how fluctuation-dependent coexistence can buffer ecosystem functioning against increasing environmental variability by promoting species richness and portfolio effects.
Our work provides a general explanation for variation in observed diversity-stability relationships and highlights the importance of conserving regional species pools to help buffer ecosystems against predicted increases in environmental variability.
\vspace{2em}
\end{abstract}

@@

However, the ability of biodiversity-ecosystem functioning (BEF) experiments to accurately represent real-world dynamics is debated [@Wardle2016; @Eisenhauer2016].
Much of the debate centers around the fact that BEF experimental protocols do not allow species gains to offset species losses.
Theoretical work on diversity-stability relationships typically suffers from the same limitation: it recognizes the role of environmental variability in driving population fluctuations which destabilize ecosystems, but ignores the potential for environmental variability to promote species richness and thereby help stabilize ecosystems [Loreau 2010, but see @Chesson2001].

@@

MATERIALS AND METHODS
---------------------
###  Consumer-resource model
We developed a semi-discrete consumer-resource model that allows many species to coexist on one resource by either the storage effect or relative nonlinearity. 
In our model, the consumer can be in one of two-states: a dormant state $D$ and a live state $N$.
The dormant state could represent, for example, the seed bank of an annual plant.
Transitions between $N$ and $D$ occur at discrete intervals $\tau$ with continuous-time consumer-resource dynamics between discrete transitions. 
Thus, our model is formulated as "pulsed differential equations" [@Pachepsky2008; @Mailleret2009; @Mordecai2016]. 
For clarity we refer to $\tau$ as years and the growing time between years as seasons with daily ($t$) time steps.

@@

\begin{align}
\frac{\text{d}N_{i}}{\text{d}t} &= \epsilon_if_{i}(R)N_{i}, \quad t \ne \tau_k\\
\frac{\text{d}R}{\text{d}t} &= - \sum\limits_{i}f_{i}(R)N_{i}, \quad t \ne \tau_k
\end{align}

@@

\noindent where $D(\tau_k)$, $N(\tau_k)$, and $R(\tau_k)$ are the abundances of each state at the end of growing season *k* and $\tau_k^+$ denotes the beginning of growing season $k$. 
The activation of dormant biomass to live biomass is controlled by $\gamma$, which is year (*k*) and species (*i*) specific.
Dormant biomass is equal to a constant fraction ($\alpha$) of live biomass at the end of the previous season ($N_{i}(\tau_k)$), plus survival ($1-\eta_i$) of dormant biomass ($D_{i}(\tau_k)$) at the end of the previous year and dormant biomass remaining after live biomass activation ($D_{i}(\tau_k)(1-\gamma_{i,\tau_k})$).
Live biomass is equal to newly activated dormant biomass ($\gamma_{i,t}D_{i}(\tau_k)$), minus some fraction of live biomass that is converted to dormant biomass ($(1-\alpha_i)N_{i}(\tau_k)$)
We assume the resource pool is not replenished within a growing season.
Resource replenishment occurs between growing seasons, and the resource pool (*R*) at the start of the growing season *k*+1 is $R(\tau_k^+) = R^+$, where $R^+$ is a random resource pulse drawn from a log-normal distribution with mean $\mu(R^+)$ and standard deviation $\sigma(R^+)$. 
Model parameters and notation are described in Table 1.

@@

\begin{align}
\Sigma(\gamma) = 
\begin{bmatrix}
1 & \rho_{1,2} & \rho_{1,3} & \rho_{1,4} \\
\rho_{2,1} & 1 & \rho_{2,3} & \rho_{2,4} \\
\rho_{3,1} & \rho_{3,2} & 1  & \rho_{3,4} \\
\rho_{4,1} & \rho_{4,2} & \rho_{4,3} & 1  \\
\end{bmatrix}
\sigma_{E}^2
\end{align}

\noindent where $\sigma^2_{E}$ is the variance of the environmental cue and $\rho_{i,j}$ is the correlation between species *i*'s and species *j*'s transition rates. 
$\rho$ must be less than 1 for stable coexistence, and in all simulations we placed that constraint that all $\rho_{i,j}$'s are equal.
In a two-species community, the inferior competitor has the strongest potential to persist when $\rho=-1$ (perfectly uncorrelated transition rates). 
However, in a four-species community the minimum possible correlation among species is -1/3 given our constraints that all $\rho$'s are equal and that $\Sigma(\gamma)$ must be positive-definite.
We used the ```R``` function ```mvrnorm``` to generate sequences of (un)correlated variates *E* that we converted to germination rates in the 0-1 range: $\gamma = e^E / \left(1 + e^E \right)$.

@@

For example, in Fig. 1C we show two species' resource uptake curves that are relatively nonlinear.
Species B has the lowest $R^*$ and would competitively exclude species A in the absence of environmental fluctuations.
But, fluctuating resource supplies can benefit species A because it can take advantage of relatively high resource levels due its higher saturation point.
Stable coexistence is only possible, however, if each species creates a disadvantage for itself when abundant.
This occurs in our model because when a resource conservative species (e.g., species B in Fig. 1C) is abundant, resource levels will remain high for a longer period of time because its draw down of resources saturates.
Likewise, when a resource acquisitive species (e.g., species A in Fig. 1C) is abundant, it quickly draws down resources to levels that favor resource conservative species.
Such reciprocity ensures species can increase when rare and stabilizes coexistence [@Armstrong1980; @Chesson2000; @Chesson2004].

@@

Under relative nonlinearity, species' resource response curves (Fig. S1-1) reflect traits that determine the variability each species' growth through time.
"Stable" species have conservative resource uptake curves, whereas "unstable" species have highly nonlinear resource uptake curves with a large difference in growth between low and high resource availability.
Therefore, we ran two sets of simulations for relative nonlinearity: one where the species pools increased from stable to unstable species and vice versa.
For example, if species A is the most stable species and species D is the least stable we ran simulations where the species pool increased from one to four species as A then B then C then D.
We then ran simulations with that order reversed.

All simulations were run for 5,000 seasons with 100-day growing seasons. 
We averaged biomass over the growing season, and those yearly values were used to calculate total community biomass in each year.
After discarding an initial 500 seasons to reduce transient effects on our results, we calculated the coefficient of variation (*CV*) of summed species biomass through time, which represents ecosystem variability,  the inverse of ecosystem stability.
We calculated species richness as the number of species whose average biomass was greater than 1 over the course of the simulation.
Parameter values for specific results are given in figure captions.
Within-season dynamics were solved given initial conditions using the package ``deSolve`` [@Soetaert2010] in ``R`` [@Team2013].
```R``` code for our model function is in the Supporting Information Appendix S1.
All model code has been deposited on Figshare (*link*) and is available on GitHub at http://github.com/atredennick/Coexistence-Stability.

@@

When we performed species removals but held environmental variability at given levels, we found a negative diversity-variability relationship (Fig. 2B,D).
Scatter around the relationship was small for the storage effect because all species have similar temporal variances.
Therefore, regardless of species identity, having more species will always stabilize ecosystem functioning through portfolio effects.
On the contrary, scatter around the relationship was larger for relative nonlinearity (Fig. 2D) because each species has unique temporal variance depending on its resource uptake curve.
Depending on the specific combination of species, two-species communities were sometimes less variable than three-species communities.

@@

The dampening effect of fluctuation-dependent coexistence on increasing environmental variability depends on the specific traits (parameter values) of the species in the regional pool.
Asymmetric competition makes it more difficult for new species to enter the local community, but once they do enter, variability is similar (Fig. 3; compare top and bottom panels).
Relatively high competition also increases the rate at which ecosystem *CV* increases with environmental variance (Fig. S1-3).
This is because the abundance of inferior competitors is reduced and do not influence ecosystem *CV* as much as when competition is symmetric.
The correlation of species' environmental responses also mediates the relationship between environmental variance, species richness, and ecosystem *CV*: lower correlations make it easier for new species to enter the community and unique environmental responses are always stabilizing (Fig. 3).

@@

DISCUSSION
----------
Theory developed for biodiversity-ecosystem function experiments emphasizes that increases in species richness should reduce ecosystem variability. 
Consistent with theoretical expectations from models in which species coexistence is maintained by fluctuation-independent mechanisms, we produced the typical negative diversity-variability relationship (Fig. 2B,D) from a model with fluctuation-dependent species coexistence [also see @Chesson2001].
Likewise, our results from the species removal simulations are consistent with results from biodiversity-ecosystem functioning experiments showing a negative relationship between species richness and ecosystem variability.
This is encouraging because species almost certainly coexist by some combination of fluctuation-independent (e.g., resource partitioning) and fluctuation-dependent mechanisms.
By extending theory to communities where species richness is explicitly maintained by temporal variability, we have gained confidence that experimental findings are generalizable to many communities.
In other words, in local settings where environmental variability is relatively homogeneous, reductions in the number of species will reduce the stability of ecosystem functioning, regardless of how coexistence is maintained.

When we allowed a gradient of environmental variability to determine species coexistence, we discovered a positive relationship between species richness and ecosystem variability (Fig. 2A,C).
While surprising when viewed through the lens of previous theory and experimental findings, such a relationship is a direct consequence of how diversity can be maintained in fluctuating environments.
The storage effect and relative nonlinearity both require environmental fluctuations to allow niche differentiation between species pairs [@Chesson2000].
Therefore, species coexistence gains strength, for both mechanisms, as the environment becomes more variable (Fig. S1-2), but the increase in environmental variability also increases ecosystem variability.

Our results may explain why deviations from the negative diversity-variability relationship often come from observational studies [@Jiang2009].
Observational studies must rely on natural diversity gradients, and if species richness depends on environmental variability, it is entirely possible to observe positive diversity-variability relationships.
For example, Sasaki and Lauenroth (2011) found a negative relationship between species richness and the temporal stability of plant abundance (a positive diversity-variability relationship) in a semi-arid grassland.
Their data came from a six sites that were 6 km apart.
While Sasaki and Lauenroth explained their results in terms of dominant species' effects, it is also possible that each site experienced sufficiently different levels of environmental variability to influence species coexistence.
@DeClerck2006 also found a positive diversity-variability when sampling conifer richness and the variability of productivity across a large spatial gradient in the Sierra Nevada.

@@

\begin{table}[!htbp]
\footnotesize
\caption{Default values of model parameters and their descriptions. Parameters that vary depending on the mode and strength of species coexistence or depending on species competitive hierarchies are labeled as ``variable'' in parentheses. The dormant-to-live biomass transition fraction ($\gamma$) is a function of other parameters, so has no default value.}
\begin{tabular}{l l l}
\hline
Parameter & Description & Value \\
\hline
$r$ & maximum per capita growth rate & 0.2 (variable) \\
$a$ & Hill function rate parameter & 2 (variable) \\
$b$ & Hill function curvature parameter & 2.5 (variable) \\
$\epsilon$ & resource-to-biomass conversion efficiency & 0.5 \\
$\alpha$ & allocation fraction of live biomass to dormant biomass & 0.5 (variable) \\
$\gamma$ & dormant-to-live biomass transition fraction & -- \\
$\rho$ & correlation of species' response to the environment & 0 (variable) \\
$\sigma_E$ & variance of the environmental cue & 2 (variable) \\
$\eta$ & dormant biomass mortality rate & 0.1 \\
$\mu(R^+)$ & mean annual resource pulse & 20 (non-log scale) \\
$\sigma(R^+)$ & standard deviation of annual resource pulse & 0 (variable) \\
\hline
\end{tabular}
\end{table}

@@

\begin{figure}[!ht]
  \centering
      \includegraphics{./components/main_figure_hires.png}
  \caption{Variability of total community as function of species richness when coexistence is maintained by the storage effect (A,B) or relative nonlinearity (C,D). Top panels show results from simulations where environmental or resource variance determine the number species that coexist in a community. Bottom panels show results from simulations where environmental or resource variance is fixed at a level that allows coexistence of all four species, but species are removed to manipulate diversity. The top panels represent regional diversity-stability relationships across natural diversity gradients, whereas the bottom panels represent local diversity-stability relationships.}
\end{figure}

@@

\begin{figure}[!ht]
  \centering
      \includegraphics[height=4in]{./components/coexistence_stability_infographic_v2.png}
  \caption{Example of how species additions under increasing environmental variability can buffer ecosystem stability when species coexistence is fluctuation-dependent via the storage effect. Environmental variability ($\sigma^2_E$) increases linearly with time. (A) Time series of species' biomass (colored lines) in a closed community where colonization of new species is not possible and (B) its associated coefficient of variation (Rolling CV; calculated over 100-yr moving window) through time. (C) Time series of species' biomass in an open community where colonization by new species from the regional pool of four species becomes possible as environmental variation increases. The trajectory of total biomass CV in the open community (D) asymptotes at lower variability than in the closed community (B) due to the buffering effect of species richness.}
\end{figure}
